% ---- PDF management layer (optional; safe to keep) ----
\RequirePackage{pdfmanagement-testphase}
\DocumentMetadata{
  uncompress,
  lang = en-US,
  pdfstandard = ua-1
}

\documentclass[10pt,letterpaper]{article}

% ---- Engine guard: require LuaLaTeX ----
\usepackage{iftex}
\ifLuaTeX\else
  \PackageError{main}{Please compile with LuaLaTeX}{}
\fi
\usepackage{environ} % to capture environment bodies

% Measure-and-place helper: keep a block together dynamically
\newcommand{\KeepTogetherBox}[1]{%
  \par
  \begingroup
    \setbox0=\vbox{#1}%
    \dimen0=\dimexpr\ht0+\dp0\relax
    \dimen2=\dimexpr\pagegoal-\pagetotal\relax
    \ifdim \dimen2<\dimen0 \newpage \fi
    \noindent\box0\par
  \endgroup
}

% ---- Layout & fonts ----
\usepackage[margin=0.2in]{geometry}
\usepackage{setspace}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

\usepackage{fontspec}
\setmainfont{Latin Modern Roman}
\setsansfont{Latin Modern Sans}
\setmonofont{Latin Modern Mono}

% ---- Hyperlinks ----
\usepackage{hyperref}
\hypersetup{
  pdfauthor = {Grant Ovsepyan},
  pdftitle  = {Resume - Grant Ovsepyan},
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}

% ---- Lists & sections ----
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt, parsep=0pt}

\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\titlespacing*{\section}{0pt}{2pt}{0pt}

% ---- Colors (for hidden stats) ----
\usepackage{xcolor}

\newcommand{\BlockStart}[1]{\mbox{\color{white}\tiny[BEGIN #1]}}
\newcommand{\BlockEnd}[1]{\mbox{\color{white}\tiny[END #1]}}

% ---- Contact info ----
\newcommand{\FullName}{Grant Ovsepyan}
\newcommand{\ContactLine}{%
  \href{mailto:govsepya@alumni.cmu.edu}{govsepya@alumni.cmu.edu} \,|\, (608) 216-5392 \,|\,
  \href{https://www.linkedin.com/in/grant-ovs/}{linkedin.com/in/grant-ovs/} \,|\,
  \href{https://github.com/Gamgrant}{github.com/Gamgrant}
}

% ---- Counters ----
\newcounter{experiencecount}
\newcounter{projectcount}
\newcounter{skillcount}

% ---- Tight bullets (no tagging) ----
% ---- Tight bullets (extra snug) ----
% ---- Tight bullets (ultra snug) ----
\newenvironment{tightbullets}
  {\begin{itemize}[
      leftmargin=*,
      nosep,
      topsep=0pt,
      partopsep=0pt,
      parsep=0pt,
      itemsep=0pt,        % no extra space between bullets
      before=\vspace{-10pt}, % pull 1st bullet up toward the line above
      after=\vspace{-2pt}
  ]}
  {\end{itemize}}

% ----- Auto-ID wrappers (generic ordinal IDs) -----
% Experience: auto tag as exp:1, exp:2, ...
\newcommand{\entryauto}[5]{%
  \edef\thisid{exp:\number\numexpr\value{experiencecount}+1\relax}%
  \KeepTogetherBox{%
    \BlockStart{\thisid}%
    \entry{#1}{#2}{#3}{#4}{#5}%
    \BlockEnd{\thisid}%
  }%
}

% Project: dynamic, unbreakable block
\newcommand{\projectauto}[3]{%
  \edef\thisid{pr:\number\numexpr\value{projectcount}+1\relax}%
  \KeepTogetherBox{%
    \BlockStart{\thisid}%
    \project{#1}{#2}{#3}%
    \BlockEnd{\thisid}%
  }%
}

% Skills: dynamic, unbreakable entire section
\NewEnviron{skillsauto}{%
  \edef\thisid{sk:\number\numexpr\value{skillcount}+1\relax}%
  \KeepTogetherBox{%
    \BlockStart{\thisid}%
    \BODY
    \BlockEnd{\thisid}%
  }%
}

% ---- Section header with hrule (Overleaf look) ----
\newcommand{\BeginSection}[1]{%
  \vspace{1pt}\section*{#1}\vspace{1pt}\hrule\vspace{2pt}%
}

% ---- Header (name + contact) ----
\newcommand{\Header}{%
  {\LARGE \textbf{\FullName}}\\[-1pt]
  {\small \ContactLine}
}

% ---- Experience entry ----
% #1 Company  #2 Role  #3 Location  #4 Dates  #5 Bullets (tightbullets)
\newcommand{\entry}[5]{%
  \stepcounter{experiencecount}%
  \textbf{#1}\hfill\textit{#3}\\
  \emph{#2}\hfill #4\\[-1pt]
  #5
  \vspace{5pt}
}

% ---- Project entry ----
% #1 Title  #2 Tech  #3 Bullets (tightbullets)
\newcommand{\project}[3]{%
  \stepcounter{projectcount}%
  \textbf{#1} \,|\, \textit{#2}\\[-1pt]
  #3
  \vspace{5pt}
}

% ---- Skills row ----
\newcommand{\skillrow}[2]{%
  \stepcounter{skillcount}%
  \textbf{#1:} #2\\
}

% ---- Embedded counts (no tags) ----
\newcommand{\EmbedCounts}{%
  {\color{white}\tiny \mbox{RESUME-STATS skills=\arabic{skillcount} projects=\arabic{projectcount} experiences=\arabic{experiencecount}}}%
}

% ---- Document ---------------------------------------------------------------
\begin{document}
\Header

% ===== Education =====
\BeginSection{Education}
\textbf{Carnegie Mellon University} \hfill Pittsburgh, PA\\
M.S. in Artificial Intelligence Engineering \;|\; GPA: 3.81/4.00 \hfill Dec 2024\\
Relevant: NLP, Modern LLMs, Retrieval \& RAG, Distributed Systems, Data Engineering

\medskip
\textbf{University of Wisconsin–Madison} \hfill Madison, WI\\
B.S. in Computer Science and B.S. in Chemical Engineering \;|\; GPA: 3.6/4.0 \hfill Aug 2023

% ===== Experience =====
\BeginSection{Experience}

\entryauto
{Medical Weight Loss Consultants (MWLC)}
{AI/ML Engineer}
{Remote, US}
{Feb 2025 -- Aug 2025}
{%
  \begin{tightbullets}
    \item Built OCR/NLP/CV pipelines + evals that lifted conversion 7× (2\% $\rightarrow$ 14\%) and cut spend 35\%; shipped dashboards and forecasting with tracked drift/latency.
    \item Built prompt-engineered agents for script/voiceover generation and a Streamlit + SQL performance dashboard; reduced wasted spend 35\% by flagging underperformers.
    \item Developed forecasting (Prophet, regression baselines) for CTR/revenue, cutting error 22\% (MAPE).
  \end{tightbullets}
}

\entryauto
{GE Healthcare (Codeworks LLC)}
{Software Developer Intern}
{Waukesha, WI}
{May 2024 -- Aug 2024}
{%
  \begin{tightbullets}
    \item Automated C++/Python CI/QA (CMake/Jenkins) across 3 OSs, reducing build time 15\% and accelerating MRI workflow iteration.
    \item Implemented early statistical quality checks to flag k-space smear 5 min earlier, improving reliability of Orchestra SDK releases.
  \end{tightbullets}
}

\entryauto
{Mandli Communications}
{Software/Systems Intern}
{Fitchburg, WI}
{Jan 2023 -- Jul 2023}
{%
  \begin{tightbullets}
    \item Fine-tuned CLRNet on proprietary data, boosting lane-detection F1 by 15\% over the baseline.
    \item Engineered ROS2/WebSocket LiDAR streaming pipeline handling 1.4M pts/sec with $\sim$50 ms latency for real-time point-cloud evaluation.
  \end{tightbullets}
}

\entryauto
{Koch Industries}
{Data/ML Intern}
{Rosemount, MN}
{May 2022 -- Aug 2022}
{%
  \begin{tightbullets}
    \item Built XGBoost/Decision-Tree anomaly classifiers and calibrated thresholds to hold recall constant; precision +12\%, false positives down; published to interactive dashboards.
    \item Forecasted equipment condition with ARIMA/VAR/Prophet using rolling time-series CV; enabled proactive maintenance and cut unplanned downtime 8\%.
    \item Built PySpark ETL ingesting 40M+ rows/day to AWS S3, with cleaning, imputation, and feature prep for ML.
  \end{tightbullets}
}

\entryauto
{Additive Manufacturing (Boydston Lab)}
{Research Assistant}
{Madison, WI}
{Jan 2019 -- Mar 2023}
{%
  \begin{tightbullets}
    \item Ran 1TB+ COMSOL heat-transfer simulations; reframed outputs in polar coordinates for distributional error analysis.
    \item Trained XGBoost surrogate regressors with k-fold CV (optimized for MAE/RMSE), cutting runtime 70\% and achieving $\sim$100× lower dimensional error in topology optimization.
    \item Co-authored \href{https://www.nature.com/articles/s41467-024-48159-7}{Nature Communications paper}.
  \end{tightbullets}
}

% ===== Projects =====
\BeginSection{Projects}

\projectauto
{RAG QA System}
{LLaMA-3, Mistral, DeepSeek, LangChain, Pinecone}
{%
  \begin{tightbullets}
    \item Built RAG QA over a CMU/Pittsburgh corpus with LangChain (Pinecone + Chroma); retrieval \& answer evals lifted LLaMA-3 F1 from 0.28 $\rightarrow$ 0.45.
    \item Built dynamic scrapers (Selenium, BeautifulSoup) that expand hidden sections, traverse lazy-loaded lists/paged views, and OCR PDFs.
    \item Designed hierarchical metadata for filtering and built an evaluation harness with 150 labeled questions.
  \end{tightbullets}
}

\projectauto
{FIFA Performance Prediction}
{PySpark, SparkML, PyTorch, GCP (BigQuery, Dataflow), PostgreSQL}
{%
  \begin{tightbullets}
    \item GCP data pipeline across 8 datasets, 100+ features, millions of rows with schema validation and optimized queries.
    \item Trained Random Forest, SVM, PyTorch NN on a 32 GB Dataproc cluster; RMSE 1.51 $\rightarrow$ 1.10 ($-27\%$).
    \item Automated hyperparameter tuning via Spark MLlib, improving runtime efficiency by 40\%.
  \end{tightbullets}
}

\projectauto
{Audio-Guided Album Cover Generation}
{CLIP, Stable Diffusion 1.4, PyTorch}
{%
  \begin{tightbullets}
    \item Built ETL scraper (1980–2024) across YouTube/Wikipedia + Spotify API (requests/BS4/pandas + multithreading) with schema checks and retry/backoff.
    \item Shipped dashboards (Streamlit) to audit ingestion \& outputs—coverage by year/genre, API error rates/latency, and side-by-side comparisons for QA.
    \item Fused multimodal signals—CLIP text + audio embeddings via cross-attention/ControlNet—and packaged train/inference pipelines for reproducible runs.
  \end{tightbullets}
}

\projectauto
{Mini-LLAMA (42M params)}
{PyTorch, Transformers}
{%
  \begin{tightbullets}
    \item Implemented Transformer blocks: RoPE, attention, optimizer in PyTorch; pretrained on TinyStories.
    \item Fine-tuned with classification heads, reaching 85\% accuracy (SST-5, CFIMDB).
  \end{tightbullets}
}

% ===== Skills =====
\BeginSection{Skills}
\begin{skillsauto}
\skillrow{Languages}{Python, C++, SQL, TypeScript}
\skillrow{CV \& OCR}{OpenCV, PyTorch, CLIP; layout-aware OCR (PaddleOCR/DocTR), Tesseract; image preprocessing \& QA}
\skillrow{LLMs}{Transformers, LoRA/QLoRA, RAG, prompt engineering; LangChain/CrewAI}
\skillrow{Data \& ETL}{PySpark, Airflow; BeautifulSoup/requests; pandas/NumPy; schema validation; Spotify/YouTube APIs}
\skillrow{Dashboards \& Web}{Streamlit; Node.js/Next.js; REST/webhooks}
\skillrow{Cloud/Infra}{AWS (ECS/EC2/S3/Lambda/API GW), Docker, CI/CD, MLflow, Linux}
\end{skillsauto} 

% ===== Embedded machine-readable counts =====
\EmbedCounts

\end{document}
